---
title: "Data_Analysis_JRME"
author: "Sebastian Robledo"
date: "6/25/2021"
output: html_document
---

# Creating the environment 

```{r}
library(lavaan)
library(here)
library(tidyverse)
library(semTools)
library(stargazer)
library(psych)
library(GPArotation)
library(semPlot)
library(MVN)
library(corrr)
library(performance)
library(tidymodels)
library(moderndive)
```

# Getting data 

```{r}
data_jrme <- 
  read.csv(here("data",
                "jrme_data_all.csv")) |> 
  mutate(Net_Str = constraint_sc)
```

# Try 4

```{r}
data_jrme_mod_4 <- 
  semTools::indProd(data_tidied_1,
                    var1 = c("NET_Q1_tr", "NET_Q2_tr", "NET_Q3_tr", "NET_Q4_tr"),
                    var2 = c("ME_Q1_tr","ME_Q2_tr", "ME_Q3_tr", "ME_Q4_tr"),
                    match = FALSE,
                    meanC = TRUE,
                    residualC = FALSE,
                    doubleMC = TRUE)
```

```{r}
data_jrme_mod_4 |>
  select(60:75) |> 
  names()
```


Model

```{r}
networking_model_mod_4 <- 
  "# measurement model
   networking_jrme =~ NET_Q1_tr + NET_Q2_tr + NET_Q3_tr + NET_Q4_tr
   effectuation <~ ME_Q1_tr + ME_Q2_tr + ME_Q3_tr + ME_Q4_tr
   net_structure =~ constraint
   # interaction term
   networkingeffectuation =~  NET_Q1_tr.ME_Q1_tr + NET_Q1_tr.ME_Q2_tr + NET_Q1_tr.ME_Q3_tr + NET_Q1_tr.ME_Q4_tr +
                              NET_Q2_tr.ME_Q1_tr + NET_Q2_tr.ME_Q2_tr + NET_Q2_tr.ME_Q3_tr + NET_Q2_tr.ME_Q4_tr +
                              NET_Q3_tr.ME_Q1_tr + NET_Q3_tr.ME_Q2_tr + NET_Q3_tr.ME_Q3_tr + NET_Q3_tr.ME_Q4_tr +
                              NET_Q4_tr.ME_Q1_tr + NET_Q4_tr.ME_Q2_tr + NET_Q4_tr.ME_Q3_tr + NET_Q4_tr.ME_Q4_tr
   # regressions
   net_structure ~ networking_jrme + networkingeffectuation
   # residual correlations"
```


Model fit 

```{r}
networking_fit_mod_4 <- 
  sem(model = networking_model_mod_4, 
      data = data_jrme_mod_4)
```

Table 

```{r}
parameterestimates(networking_fit_mod_4,
                   standardized = TRUE) |> 
  filter(op == "~") |> 
  mutate(stars = ifelse(pvalue < 0.001, "***",
                        ifelse(pvalue < 0.01, "**",
                               ifelse(pvalue < 0.05, "*", "")))) |> 
  select(LHS = lhs, RHS = rhs, Coefficient = est, 
         Z = z, "p-value" = pvalue, Sig. = stars) |> 
  stargazer(type = "text", title = "Regression Coefficients", 
            summary = FALSE, digits = 3, 
            digits.extra = 0, rownames = FALSE)
```

The model's outputs are poor. We need to improve the relationship between networking and net_structure. I want to see the correlations. 

```{r}
data_tidied_1 |> 
  rowwise() |> 
  mutate(networking_mean_raw = mean(c(NET_Q1, NET_Q2, NET_Q3, NET_Q4))) |> 
  select(networking_mean, networking_mean_raw, constraint, density, clustering) 
```

What if we remove items?. For example, items with 0 standard deviation?

```{r}
data_tidied_2 <- 
  data_tidied_1 |> 
  rowwise() |> 
  mutate(networking_sd = sd(c(NET_Q1, NET_Q2, NET_Q3, NET_Q4)),
         effectuation_sd = sd(c(ME_Q1, ME_Q2, ME_Q3, ME_Q4))) |> 
  filter(networking_sd == 0) |> 
  filter(effectuation_sd == 0)
```

```{r}
data_tidied_2 |> 
  rowwise() |> 
  mutate(networking_mean_raw = mean(c(NET_Q1, NET_Q2, NET_Q3, NET_Q4))) |> 
  select(networking_mean, networking_mean_raw, constraint, density, clustering) |> 
  correlate()
```

Checking the regression model 

```{r}
df_1 <- 
  data_tidied_1 |> 
  rowwise() |> 
  mutate(networking_mean_raw = mean(c(NET_Q1, NET_Q2, NET_Q3, NET_Q4))) |>
  select(networking_mean, constraint)

model_1 <- 
  linear_reg() |> 
  set_engine("lm") |> 
  fit(constraint ~ networking_mean, df_1)

model_2 <- lm(constraint ~ networking_mean, df_1)

get_regression_table(model_2)
```
Checking the model

```{r}
performance::check_model(model_2)
```



# Try 3

```{r}
data_jrme_mod_3 <- 
  semTools::indProd(data_tidied_1,
                    var1 = c("NET_Q1_tr", "NET_Q2_tr", "NET_Q3_tr", "NET_Q4_tr"),
                    var2 = c("ME_Q2_tr", "ME_Q3_tr", "ME_Q4_tr"),
                    match = FALSE,
                    meanC = TRUE,
                    residualC = FALSE,
                    doubleMC = TRUE)
```

Model 

```{r}
networking_model_mod_3 <- 
  "# measurement model
   networking_jrme =~ NET_Q1_tr + NET_Q2_tr + NET_Q3_tr + NET_Q4_tr
   effectuation =~ ME_Q2_tr + ME_Q3_tr + ME_Q4_tr
   net_structure =~ constraint
   # interaction term
   networkingeffectuation =~ NET_Q1_tr.ME_Q2_tr + NET_Q1_tr.ME_Q3_tr + NET_Q1_tr.ME_Q4_tr +
                             NET_Q2_tr.ME_Q2_tr + NET_Q2_tr.ME_Q3_tr + NET_Q2_tr.ME_Q4_tr +
                             NET_Q3_tr.ME_Q2_tr + NET_Q3_tr.ME_Q3_tr + NET_Q3_tr.ME_Q4_tr +
                             NET_Q4_tr.ME_Q2_tr + NET_Q4_tr.ME_Q3_tr + NET_Q4_tr.ME_Q4_tr
   # regressions
   net_structure ~ networking_jrme + effectuation + networkingeffectuation
   # residual correlations"
```


Model fit 

```{r}
networking_fit_mod_3 <- 
  sem(model = networking_model_mod_3, 
      data = data_jrme_mod_3)
```

Table 

```{r}
parameterestimates(networking_fit_mod_3,
                   standardized = TRUE) |> 
  filter(op == "~") |> 
  mutate(stars = ifelse(pvalue < 0.001, "***",
                        ifelse(pvalue < 0.01, "**",
                               ifelse(pvalue < 0.05, "*", "")))) |> 
  select(LHS = lhs, RHS = rhs, Coefficient = est, 
         Z = z, "p-value" = pvalue, Sig. = stars) |> 
  stargazer(type = "text", title = "Regression Coefficients", 
            summary = FALSE, digits = 3, 
            digits.extra = 0, rownames = FALSE)
```


# Try 2

http://www.koreascience.or.kr/article/JAKO201919059190001.view

```{r}
data_jrme_mod <- 
  semTools::indProd(data_tidied_1,
                    var1 = c("NET_Q1", "NET_Q2", "NET_Q3", "NET_Q4"),
                    var2 = c("ME_Q2", "ME_Q3", "ME_Q4"),
                    match = FALSE,
                    meanC = TRUE,
                    residualC = FALSE,
                    doubleMC = TRUE)
```

New variables

```{r}
data_jrme_mod |> 
  select(48:59) |> 
  names()
```

Model 

```{r}
networking_model_mod <- 
  "# measurement model
   networking_jrme =~ NET_Q1 + NET_Q2 + NET_Q3 + NET_Q4
   effectuation =~ ME_Q2 + ME_Q3 + ME_Q4
   net_structure =~ constraint
   # interaction term
   networkingeffectuation =~ NET_Q1.ME_Q2 + NET_Q1.ME_Q3 + NET_Q1.ME_Q4 +
                             NET_Q2.ME_Q2 + NET_Q2.ME_Q3 + NET_Q2.ME_Q4 +
                             NET_Q3.ME_Q2 + NET_Q3.ME_Q3 + NET_Q3.ME_Q4 +
                             NET_Q4.ME_Q2 + NET_Q4.ME_Q3 + NET_Q4.ME_Q4
   # regressions
   net_structure ~ networking_jrme + effectuation + networkingeffectuation
   # residual correlations"
```

Model fit 

```{r}
networking_fit_mod <- 
  sem(model = networking_model_mod, 
      data = data_jrme_mod)
```


```{r}
summary(networking_fit_mod, standardized = TRUE)
```


```{r}
parameterestimates(networking_fit_mod, standardized = TRUE)
```
```{r}
parameterestimates(networking_fit_mod, standardized = TRUE) |> 
  filter(op == "~") |> 
  mutate(stars = ifelse(pvalue < 0.001, "***",
                        ifelse(pvalue < 0.01, "**",
                               ifelse(pvalue < 0.05, "*", "")))) |> 
  select(LHS = lhs, RHS = rhs, Coefficient = est, 
         Z = z, "p-value" = pvalue, Sig. = stars) |> 
  stargazer(type = "text", title = "Regression Coefficients", 
            summary = FALSE, digits = 3, 
            digits.extra = 0, rownames = FALSE)
```


# Try 1

## Moderating effect

Creating the interaction term between networking and effectuation

```{r}
data_jrme_modet <- 
  data_jrme |> 
  mutate(networking_x_effectuation = networking * modelo_efectual)
```

Parameters

```{r}
moderation_model <- "
  # regressions
  Net_Str ~ b1*networking
  Net_Str ~ b2*modelo_efectual
  Net_Str ~ b3*networking_x_effectuation
  
  modelo_efectual ~ modelo_efectual.mean*1
  
  modelo_efectual ~~ modelo_efectual.var*modelo_efectual
  
  SD.below := b1 + b3*(modelo_efectual.mean - sqrt(modelo_efectual))
  mean := b1 + b3*(modelo_efectual)
  SD.above := b1 + b3*(modelo_efectual.mean + sqrt(modelo_efectual))
  "


EffecModel_jrme <- "
                    
                    networking ~ modelo_efectual
                    Net_Str ~ networking
                    "
```


```{r}
sem1 <- 
  cfa(EffecModel_jrme, data = data_jrme_modet)
```

```{r}
summary(sem1, fit.measures=TRUE, standardized=T,rsquare=T)
```

