---
title: "Effectuation Paper"
output: html_notebook
---

Summary

```{r}
data_paper <- read_csv("Data/Networking como una herramienta del Modelo Efectual_3.csv")
dim(data_paper)
```

We scale constrain metric

```{r}
data_paper$constraint_sc <- scale(data_paper$constraint)
```

```{r}
EffecModel <- "Effectuation =~ ME_Q2 + ME_Q3 + ME_Q4
               Networking =~ NET_Q1 + NET_Q2 + NET_Q4
               WOM   =~ WOM_Q1 + WOM_Q2 + WOM_Q3
               Net_Str =~ constraint_sc
               Performance =~ DESEM_Q1 + DESEM_Q2 
               Performance ~ Effectuation 
               Performance ~ Net_Str
               Performance ~ WOM
               Effectuation ~ Networking
               Net_Str ~ Networking
               WOM ~ Networking"
```

Grados de libertad

Degrees of Freedom (df)

- Determined by the number of manifest variables and estimated values
- df = Possible Values - Estimated Values
- Possible Values = Manifest Variables * (Manifest Variables + 1) / 2



degrees of freedom (parameters – available covariances and variances)

Tenemos 12 variables observadas 

available covariances and variances - (12 * (12+1)/2)= 78

parameters:

Lambdas: 2 + 2 + 2 + 0 + 1 = 7  (free loadings)

Thetas (error variances) = 12

Latent variables = 5

Paths = 6

Total = 7 + 12 + 5 + 6 = 30 # there is a mistake

For more fit measures see http://davidakenny.net/cm/fit.htm

Creating the fitted model

```{r}
Effec.fit <- lavaan::cfa(EffecModel, data=data_paper)
```

Inspecting the factor loading for each item

```{r}
inspect(Effec.fit, what = "std")$lambda
```

Visualing the results

```{r}
summary(Effec.fit, fit.measures=TRUE, standardized=T,rsquare=T)
```

```{r}
fitMeasures(Effec.fit)
```

```{r}
semTools::reliability(Effec.fit)
```

```{r}
modificationindices(Effec.fit, sort. = TRUE)
```

